%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% !TEX program = xelatex
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
% Personalized by: Lewis Guignard
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4
%\usepackage[hidelinks]{hyperref}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Lewis}{Guignard}{ % Your name
% \urlstyle{same}\url{http://diffusecreation.com} \\
\href{mailto:lewisguignard@gmail.com}{lewisguignard@gmail.com} | 980.875.8786 | \href{https://www.linkedin.com/in/lguignard}{\bf LinkedIn} \\
% Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{General}

Estimation / Inference\\
Amazon AWS\\
Micro-service Architectures\\
Technical Sales\\
Training / Presentations\\

\sectionspace % Some whitespace after the section

\subsection{Programming / DevOps}

\location{Proficient:}
\textbullet{} Python \textbullet{} MySql\\
\textbullet{} Linux (debian/bash/zsh) \textbullet{} hjkl\\
\textbullet{} git \textbullet{} gitlab \textbullet{} jira\\
\location{Amateur:}
\textbullet{} Matlab \textbullet{} \LaTeX\ \textbullet{} Java \textbullet{} C++\\
\location{Competent:}
\textbullet{} R \textbullet{} .html/.css/.js\\

\sectionspace % Some whitespace after the section


%------------------------------------------------
% Education
%------------------------------------------------

\section{Education}

\subsection{Stanford University}

\descript{MS Electrical Engineering}
Signal Processing, Data Science \\
\location{June 2016 | Stanford, CA \\ Cum. GPA: 3.7}

\sectionspace % Some whitespace after the section

\subsection{NCSU}
\descript{North Carolina State University}
\descript{BS Physics}
\location{2008-2011 | Raleigh, NC \\ Cum. GPA: 4.0}
Valedictorian \\


\sectionspace % Some whitespace after the section

%------------------------------------------------



%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

\subsection{Graduate}

Machine Learning \\
Convex Optimization \\
Signal Processing \\
Fourier Analysis \\
Linear Algebra \\

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Undergraduate}

Solid State Physics \\
Modeling / Simulation \\


\sectionspace % Some whitespace after the section



\section{Interests}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space

3D Printing | Raspberry Pi | Radio (KM4JQU) |  Visualization | Cycling | Photography | Backpacking


\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page


%------------------------------------------------
% Projects
%------------------------------------------------

\section{Summary}

A highly organized, creative data science professional with over 6 years of progressive analysis and prediction experience.  Proficiency in full data science pipeline: researching and purchasing data sources, cleansing and quality control, model creation and validation, creating stable and enterprise ready code-base, delivering insights to leadership team.  Expert in public speaking and simplifying highly technical concepts.  Adept in training and integrating teams of individuals of varying experience.  


%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\sectionspace % Some whitespace after the section
% \runsubsection{Corax Cyber}
\runsubsection{\href{https://www.coraxcyber.com}{\bf Corax Cyber}}
\descript{Head of Data Science}
\location{Mar 2016 - Current | SF, CA}
\vspace{\topsep}
\begin{tightitemize}
\item Builds models to predict frequency and severity of cyber breach and business interruption events \textbullet{}  Leads a team of datascientists \textbullet{} Manage estimation projects \textbullet{} Technical sales and speaking \textbullet{} Seek out, negotiate, and ingest new data-sources \textbullet{} Manage ~100M daily record ingestion and analysis
\end{tightitemize}

\sectionspace % Some whitespace after the section
\runsubsection{\href{https://industries.ul.com/lighting}{\bf Underwriters Laboratories}}
% \runsubsection{Underwriters Laboratories}
\descript{Engineer}
\location{Oct 2011 - Aug 2014 | Durham, NC}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Critiqued LED Luminaires, modules and power supplies for compliance to relevant UL or IEC international standards. Designed and analyzed test plans for product performance.
\end{tightitemize}


%------------------------------------------------

\sectionspace % Some whitespace after the section
% \runsubsection{Helmholtz Zentrum Berlin}
\runsubsection{\href{https://www.helmholtz-berlin.de/index_en.html}{\bf Helmholtz Zentrum Berlin}}
\descript{Visiting Scientist}
\location{Jun 2011 - Sep 2011 | Berlin, Germany}
\begin{tightitemize}
\item Experimented in photo-electrochemical systems, semiconductor-electrolyte interfaces and nanoemitters. Focus on photovoltaic science and photo-induced Carbon Dioxide reduction.
\end{tightitemize}

\sectionspace % Some whitespace after the section





\sectionspace % Some whitespace after the section



%------------------------------------------------
% Publications | Awards | Societies
%------------------------------------------------

\section{Patents | Publications | Awards}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item {\bf Patents: \href{https://patents.google.com/patent/US20180069889A1/en?oq=US20180069889A1}{US20180069889A1} \href{https://patents.google.com/patent/US20180124092A1/en?oq=US20180124092A1}{US20180124092A1}}
\item \href{https://pubs.acs.org/doi/abs/10.1021/jz101276h}{\bf B. A. Collins, E. Gann, X. He, L. Guignard, C. R. McNeill, H. Ade. Molecular Miscibility of Polymer}
− Fullerene Blends. The Journal of Physical Chemistry Letters 0, 3160-3166

\item \href{http://cs229.stanford.edu/proj2015/010_report.pdf}{\bf Machine Learning}: Created a 93.1 \% accurate musical instrument classifier.
\item Lean Six Sigma Green Belt Training | Lean Leader Training
\item Phi Beta Kappa | Phi Kappa Phi | Sigma Pi Sigma (National Physics Honor Society)
\item Speaker: American Physical Society Meeting 2010 / Net Diligence Santa Monica, CA 2018 / Catastrophe Risk London 2019 
\item FIRST Robotics volunteer, 2 seasons
\end{tightitemize}


\sectionspace % Some whitespace after the section


%------------------------------------------------
% Research
%------------------------------------------------

\section{Research}

\runsubsection{North Carolina State University}
\descript{| Researcher}

\location{Oct 2008 - Jun 2011| Raleigh, NC}
Investigated organic photo-voltaic system dynamics, focusing on efficiency, morphology, material properties. Controlled laboratory equipment, including purchasing, troubleshooting and repairs.  Managed several group and individual experiments in parallel. Data collection,
analysis, image processing, and presentation.
%------------------------------------------------
% Societies
%------------------------------------------------


%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}